Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-16 paper/us_election_2020.qmd
changes
resolve reference issues and minor changes

Our dataset's quantitative representation of real-world phenomena is influenced by several factors, which inherently limit the accuracy of our measurements for the five variables.

@@

Finally, for "employ", indicating the respondent's self-reporting employment status, can be influenced by various factors such as job changes, seasonal work, and personal circumstances. In addition, individuals may intentionally misreport their employment status due to societal pressures or to access benefits. For instance, some may falsely claim employment to avoid stigma, while others may report unemployment to qualify for unemployment benefits. Additionally, students working part-time jobs may selectively report their status based on their perceived benefit. These discrepancies can introduce bias and inaccuracies into the data, impacting the reliability of our analyses.

@@

Conversely, we anticipate a negative relationship between voters in the South and Midwest regions and support for Biden. These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump. States such as Texas and Florida, which are known Republican strongholds, are located in the South. Therefore, individuals in these regions may be less inclined to support Biden's progressive agenda.

@@

The trace plot in @fig-trace does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-rhat), we can observe that everything is close to 1, and no more than 1.05, which shows the great convergence of Markov chain Monte Carlo for our model.

@@

## Credibility Interval {#sec-credibility-interval}
90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.

>>>>

Because our dataset is survey-based, the measurement accuracy of our five variables might be influenced by many external factors.

@@

Finally, for "employ", indicating the respondent's self-reporting employment status, can be influenced by various factors such as job changes, seasonal work, and personal circumstances. In addition, individuals may intentionally misreport their employment status due to societal pressures or to access benefits. For instance, some may falsely claim employment to avoid stigma, while others may report unemployment to qualify for unemployment benefits. Additionally, students working part-time jobs may selectively report their status based on their perceived benefit. These inconsistencies can introduce bias and inaccuracies into the data, impacting the reliability of our analyses.

@@

Conversely, we anticipate a negative relationship between voters in the South and Midwest regions and support for Biden. These regions have a stronger conservative presence and a history of supporting Republican candidates like Trump. States, such as Texas, which are known Republican strongholds, are located in the South. Therefore, individuals in these regions may be less inclined to support Biden's progressive agenda.

@@

The trace plots in @fig-trace1, @fig-trace2, and @fig-trace3 do not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-rhat), we can observe that everything is close to 1, and no more than 1.05, which shows the great convergence of Markov chain Monte Carlo for our model.

@@

## Credibility Interval {#sec-credibility-interval}
